\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-10-22 main.tex
Updates from Overleaf

\begin{figure}
\centering
\begin{subfigure}{0.75\textwidth}
    \centering
    \includegraphics[width=\textwidth]{examples/images/simply_connected_region.png}
    \caption{The fluxoid $\Phi^f_S$ vanishes for simply-connected regions containing no vortices.}
    \label{fig:fluxoid-simply}
\end{subfigure}

\begin{subfigure}{0.75\textwidth}
    \centering
    \includegraphics[width=\textwidth]{examples/images/simply_connected_region_with_vortices.png}
    \caption{The fluxoid $\Phi^f_S$}
    \label{fig:fluxoid-simply-vortices}
\end{subfigure}

\begin{subfigure}{0.75\textwidth}
    \centering
    \includegraphics[width=\textwidth]{examples/images/multiply_connected_region.png}
    \caption{Multiply-connected region}
    \label{fig:fluxoid-multiply}
\end{subfigure}

>>>>

\begin{figure}
\centering
\begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{examples/images/simply_connected_region.png}
    \caption{The fluxoid $\Phi^f_S$ vanishes for simply-connected regions containing no vortices. Current density $|\vec{J}|$ (a) and out-of-plane field $\mu_0H_z$ (b) for the square ring with $\Lambda=1\,\mu\mathrm{m}$ subject to a uniform applied field of 0.1 mT. The ``flux part'' and ``supercurrent part`` of the fluxoid are shown as filled and unfilled bars respectively in (c), with the colors corresponding to the colors of the paths in (a, b).}
    \label{fig:fluxoid-simply}
\end{subfigure}

\begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{examples/images/simply_connected_region_with_vortices.png}
    \caption{The fluxoid $\Phi^f_S$}
    \label{fig:fluxoid-simply-vortices}
\end{subfigure}

\begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{examples/images/multiply_connected_region.png}
    \caption{Multiply-connected region}
    \label{fig:fluxoid-multiply}
\end{subfigure}
